% !TEX root = thesis-en.tex

\chapter{Introduction}
\label{intro}

% move notes to the last of the chapter in Chicago style
\makeendnotes

Keio University Graduate School of Media Design
(KMD)\footnote{\url{http://www.kmd.keio.ac.jp}} was established
to train talented individuals to work on the global stage building and
running new industries for the coming ``creative society,''
a world in which the driving force of the economy will be creativity
rather than productivity or efficiency.
``Creativity'' is the ability to produce new ideas, expressions,
and processes~\cite{Inakage2007}.
These new creations and the activities inspire give rise to
an economic base with the power and energy to bring forth innovative
technologies and enrich human societies.
The work of the individual is paramount in the creative society;
consumers lead creative activities.
Collaboration is all-important.
Individuals innovate, mutually recognizing a diversity of values
and making personal, imaginative contributions that collectively
result in extraordinary achievements and capacities.

The way in which we produce value from cultural and social resources
will change in the creative society.
Advanced digital technology provides a basis from which to redistribute
resources across the globe, and in doing so, restores the creativity of
human beings.
Technological progress produces value from creative activities
in everyday life and increases the number of creative individuals,
who produce value through their activities.
As networks expand, the barriers to redistribution of cultural and
social resources disappear, enabling resources to be shared freely.
Creativity will be a valuable activity within our day-to-day lives,
and people will fully embrace the ability to share and to express
themselves.
We are currently witnessing numerous events that hint
at the new economic activities to come.
Indeed, the fostering of the creative industries and cultural industries
that use creativity as a source of economic activity has,
in many countries, become a matter of national strategy.

At the Graduate School of Media Design, we call these future leaders
``media innovators.''
We implement projects that create media, content, and services
as international collaborations among industry, academia and government,
and in the process we train the media innovators of tomorrow.
The School features a state-of-the-art communications environment
and a broad, collaborative network
with some of the world's foremost universities.
The main campus is in Hiyoshi with satellites in Osaka and Singapore as well.
Both Japanese and English are our official languages and we welcome students
from around the globe.
Together with our highly experienced and insightful faculty members,
students learn the skills they need to lead the creative society
in this diverse community.

Media innovators harmonize and integrate skills in the four basic areas
of design creativity, technology creativity,
management creativity and policy creativity.
In addition, the curriculums are designed so that each student masters
advanced professional skills in one or two specialized areas.
It also features a practical program that we call ``Real Projects.''
These are intensely collaborative projects in which students work
with media innovators who possess different skills than they have to
address problems that impact their societies and communities,
and in the process, learn how to articulate a clear vision
and cooperate to solve the real world problems.
Our objective at the Graduate School of Media Design is to develop
leaders who will be able to combine the four creativities of design,
technology, management, and policy to drive projects on the global stage.

Through ``Real Projects'', KMD creates new media that go beyond
the parameters of conventional mass media.
This fusion of technology and media has the potential
to significantly reshape our everyday lives.
The content extends to physical artifacts and environment,
and it ultimately influences our social systems.
We learn and practice the five skills of fieldwork, strategic planning,
brainstorming, prototyping, execution, and verification as we develop,
verify, commercialize and establish companies and organizations
to exploit innovative content and technologies.
As we do so, we emphasize the global impact of our work in areas
such as standardization and institutional reform.

The Graduate School of Media Design looks forward to receiving applications
from potential students who are ambitious and passionate
about becoming media innovators and are eager to gain
the global perspective needed of the future leaders of the creative society.

% put endnotes here
\putendnotes

% Don't put anything below this line

